Optimizing Abstract$^{\text 2}$ Machines

### 2012-11-11 paper/paper.tex
Typo: comlexity

The first problem that we realized with the AAM approach was that much
of the non-determinism is spurious. For example, in a function
application,
\begin{alltt}
(f x y)
\end{alltt}

@@

Delta Store + Special + Compile + Lazy:
   cpu time: 668 real time: 686 gc time: 41

@@

This effort increases substantially as the comlexity of the analyzed
language increases.  Both the work of maintaining the concrete
semantics and constraint system (and the relations between them) must
be scaled simultaneously.  However, constraint systems, which have
been extensively studied in their own right, enjoy efficient
implementation techniques and can be expressed in declarative logic
languages that are heavily
optimized~\cite{dvanhorn:bravenboer-smaragdakis-oopsla09}.
Consequently, constraint-based analyses can be computed quickly.  For
example, Jagannathan and Wright's polymorphic splitting
implementation~\cite{dvanhorn:wright-jagannathan-toplas98} analyses
the church numeral example of figure~\ref{fig:church} in 7
milliseconds, about 25 times faster than the fastest implementation
considered here.  These analyses compute very different things (as
detailed in section~\ref{sec:accept}), so the performance comparison
is not apples-to-apples.  We view the primary contribution of this
work as a systematic path that eases the design, verification, and
implementation of analyses using the abstracting abstract machine
approach to within a factor of performant constraint-based analyses.

>>>>

The first problem that we realized with the AAM approach was that much
of the non-determinism is spurious. For example, in a function
application,
\begin{center}{\tt (f x y)}\end{center}

@@

Delta Store + Compile + Lazy:
   cpu time: 668 real time: 686 gc time: 41

@@

This effort increases substantially as the complexity of the analyzed
language increases.  Both the work of maintaining the concrete
semantics and constraint system (and the relations between them) must
be scaled simultaneously.  However, constraint systems, which have
been extensively studied in their own right, enjoy efficient
implementation techniques and can be expressed in declarative logic
languages that are heavily
optimized~\cite{dvanhorn:bravenboer-smaragdakis-oopsla09}.
Consequently, constraint-based analyses can be computed quickly.  For
example, Jagannathan and Wright's polymorphic splitting
implementation~\cite{dvanhorn:wright-jagannathan-toplas98} analyses
the church numeral example of figure~\ref{fig:church} in 7
milliseconds, about 25 times faster than the fastest implementation
considered here.  These analyses compute very different things (as
detailed in section~\ref{sec:accept}), so the performance comparison
is not apples-to-apples.  We view the primary contribution of this
work as a systematic path that eases the design, verification, and
implementation of analyses using the abstracting abstract machine
approach to within a factor of performant constraint-based analyses.
